
---
title: "Analysis of Table MEAN"
author: "f.j.Padt"
date: "Friday, April 03, 2015"
output: pdf_document
---

```{r Initialization, echo=FALSE}
library(data.table)
library("RODBC", lib.loc="~/R/R-3.1.3/library")

A2R <- odbcConnect("ACCESS2R")
dtMEAN <- as.data.table(sqlFetch(A2R, "RA1C230_MEAN", 
                                 stringsAsFactors = FALSE))

close(A2R)
```

## DUPLICATES ##

```{r DUPLICATES}
dtMEAN[, DUPLICATE:= grepl("DUPLICATE", EAN11, ignore.case = TRUE)]
(t00 <- table(dtMEAN$DUPLICATE))
cnt <- nrow()
dtMEAN <- dtMEAN[DUPLICATE == FALSE, ]
```

Number of ENA11 with "DUPLICATE": `r t00["TRUE"]`. 
These are deleted and not included in the rest of the analysis.

## HPEAN ##

The following table shows a count on EANTP and HPEAN.

```{r HPEAN,echo=FALSE}

(t01 <- table(dtMEAN$EANTP, ifelse(is.na(dtMEAN$HPEAN), "-", "X")))

```
Note there are `r t01[which(rownames(t01) == "HE"), colnames(t01) == "-"]` 
entries with EANTP = HE but which are not marked as HPEAN
(is this correct)?

## MEINH ##

The following table shows a count on the Unit of measure. 

```{r MEINH}
(t02 <- table(dtMEAN$MEINH))
```

As can be seen not everyhting is ST, is this correct?

```{r 1toN}
setkey(dtMEAN, "MATNR", "MEINH")
dtMEAN[, DUP:=duplicated(dtMEAN, by=c("MATNR", "MEINH"))]
```

```{r Other}
dtMEAN <- fread("c:/per/qryRA1C230_MEAN_Z2.txt")
dtMEAN <- dtMEAN[MEINH=="ST"]
setkey(dtMEAN, "EAN11","EANTP")

tst<-dtMEAN[duplicated(dtMEAN)]
write.table(tst, file="c:/per/duplicates.csv", row.names=FALSE, sep=";")

dtMEAN <- dtMEAN[EANTP == "Z1" & MEINH == "ST", 
                 .(MATNR, EAN11, EANTP, MEINH)]
setnames(dtMEAN, 
         c("MATNR","EAN11"),
         c("SAPNR","MATNR"))
# dtMEAN_Z1[, DM_ := duplicated(dtMEAN_Z1, by=c("MATNR"))]
# dtMEAN_Z1[, DME := duplicated(dtMEAN_Z1, by=c("MATNR", "EAN11"))]

# dtMARM_Z1 <- dtMARM[NUMTP == "Z1" & MEINH == "ST", 
#                     .(MATNR, EAN11, NUMTP, MEINH)]
# dtMARM_Z1[, DM_ := duplicated(dtMARM_Z1, by=c("MATNR"))]
# dtMARM_Z1[, DME := duplicated(dtMARM_Z1, by=c("MATNR", "EAN11"))]

library("RODBC", lib.loc="~/R/R-3.1.3/library")
ch <- odbcConnect("ACCESS2R")

close(ch)

sqlTables(ch)
sqlTables(ch, tableName = "R

tst <- sqlFetch(ch, "BD1C100_RSDIOBJT")

dfMEAN <- sqlFetch(ch, "RA1C230_MEAN")
dfMARM <- sqlFetch(ch, "RA1C230_MARM")

# sqlQuery(sh, paste("SELECT State, Murder FROM USArrests",
#                    "WHERE Rape > 30 ORDER BY Murder"))

#########################################################################

dtMARM[, TAB:="MARM"]
dtMEAN[, TAB:="MEAN"]

dtMAPPING <- dtMEAN[, .(MATNR, EAN11, EANTP, TAB)]
setnames(dtMAPPING, "EANTP", "NUMTP")

dtMAPPING <- rbind(dtMAPPING, dtMARM[, .(MATNR, EAN11, NUMTP, TAB)])
setkey(dtMAPPING, "MATNR", "TAB", "NUMTP")
dtMAPPING <- dtMAPPING[EAN11!="DUPLICATE",]


dtMAPPING[, DM__ := duplicated(dtMAPPING, by=c("MATNR"))]
dtMAPPING[, DME_ := duplicated(dtMAPPING, by=c("MATNR","EAN11"))]
dtMAPPING[, DMEN := duplicated(dtMAPPING, by=c("MATNR","EAN11","NUMTP" ))]
dtMAPPING[, DM_N := duplicated(dtMAPPING, by=c("MATNR","NUMTP" ))]

dtMAPPING[, D001 := sum(DMEN), by=c("MATNR","NUMTP")]
dtMAPPING[, D002 := sum(DM_N), by=c("MATNR","NUMTP")]

dtCHK001 <- dtMAPPING[D001  > 0]
dtCHK002 <- dtMAPPING[D001 == 0 & D002 > 0]

dtCHK003 <- dtMAPPING[D001 == 0 & D002 > 0 & NUMTP == "HE"]

dtCHK004 <- dtCHK001[DM__ & DME_ & DMEN & DM_N,]
dtMAT_Z1 <- dtCHK004[NUMTP == "Z1", ]


dtCHK006 <- dtGVBNL
setnames(dtCHK006, "article_number", "EAN11")


dtMAT_Z1[, D_E_ := duplicated(dtMAT_Z1, by=c("EAN11"))]
setkey(dtMAT_Z1, "EAN11")
setkey(dtMAT_Z1, "MATNR", "TAB", "NUMTP")
dtMAT_Z1 <- dtMAT_Z1[D_E_ != TRUE, ]

dtCHK007 <- merge(dtCHK006, dtMAT_Z1[,.(EAN11, MATNR)], by="EAN11", all.x=TRUE)
```
