
---
title: "Analysis of Table MEAN"
author: "Floris Padt & Laura Sabatini"
date: "Wednesday Apr 08"
output: word_document
---

```{r Initialization, echo=FALSE, result=TRUE}
library(data.table)
library("RODBC", lib.loc="~/R/R-3.1.3/library")
library("xlsx", lib.loc="~/R/R-3.1.3/library")

parSYST <- "RA1"
parCLNT <- "250"
parTABN <- "MEAN"
parMEAN <- paste0("qry", parSYST, "C", parCLNT, "_", parTABN, "_MARA")

file.remove(dir("./results", full.names = TRUE))
fileXL <- paste0("./results", "/wb.xlsx")

A2R    <- odbcConnect("ACCESS2R")
dtMEAN <- as.data.table(
  sqlFetch(A2R, parMEAN, 
           stringsAsFactors = FALSE)
  )[, `:=`(LVORM = NULL, MSTAE = NULL, MSTAV = NULL)]

setkey(dtMEAN, "MATNR", "MEINH")

dfCMT <- sqlQuery(A2R, 
                  paste("SELECT START, DTIME, RECORDCOUNT", 
                        "FROM zsDD02_SLCT",
                        "WHERE ((SYSTEMID=", 
                        paste0("'", parSYST, "'"),  
                        ") AND (CLIENT=", 
                        parCLNT, ") AND (TABNAME=", 
                        paste0("'", parTABN, "'"), 
                        "));")) 

attr(dtMEAN, "RefreshDate")      <- dfCMT[["START"]]
attr(dtMEAN, "RecordsExtracted") <- dfCMT[["RECORDCOUNT"]]


# dtMARM <- as.data.table(sqlFetch(A2R, "RA1C230_MARM", 
#                                  stringsAsFactors = FALSE))
# setkey(dtMARM, "MATNR", "MEINH")

dtMAPPING <- copy(dtMEAN)
# dtMAPPING <- rbind(dtMEAN)

attr(dtMAPPING, "RefreshDate")      <- dfCMT[["START"]]
attr(dtMAPPING, "RecordsExtracted") <- dfCMT[["RECORDCOUNT"]]


close(A2R)

fECHO    <- FALSE
fRESULTS <- TRUE
```

# Cleansing #

Before the mapping table (MEAN) can be analyzed for the entitiy relationships, any 
invalid records need to be excluded. The following assumptions/Checks are made on the 
validity of records:  
1. Only the Unit of Measure (UoM) of importance is: *ST*  
2. The supplier EAN (HE) is the main EAN if existing.  
3. One Supplier EAN has One SAP Article Assigned  
4. One SAP Article has 1 or N legacy Articles (1:1  or 1:N). 


## Table MEAN ##

This reproducible analysis is based upon the MEAN extracted from the ECC system. 
The data structure, recency and 10 example records of this table can be found below:

Last Extraction Date from table `r parTABN` out of `r parSYST` client `r parCLNT`:
`r attr(dtMAPPING, 'RefreshDate')`    
Number of records Extracted: `r attr(dtMAPPING, 'RecordsExtracted')`  
Number of records Analysed : `r nrow(dtMAPPING)` 

```{r EXAMPLE_MEAN, echo=FALSE, results=TRUE}
#str(dtMEAN)
dtMAPPING[1:10, .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)]
```

### MEINH ###

The following table shows a count on the Unit of measure (UoM). 

```{r MEINH, echo=fECHO, results=fRESULTS}
(tmp      <- table(dtMAPPING$MEINH))
dtMAPPING <- dtMAPPING[MEINH == "ST", ]
```

As can be seen there are `r sum(tmp) - tmp[which(row.names(tmp) == "ST")] `
other Units of Measure in the table.  
These will be excluded from the further analysis.

```{r DOUBLE_ENTRIES, echo=FALSE, results='hide'}
### DOUBLE ENTRIES ###

# The table below shows the number of double records. These records are duplicates
# of a mapping relationship per OPCO.   
# Although functional there is no issue these records should not exist.


dtMAPPING <- dtMAPPING[, DMET := duplicated(dtMAPPING, 
                                            by = c("MATNR", "EAN11", "EANTP"))]
(tmp <- table(dtMAPPING$DMET))
dtMAPPING <- dtMAPPING[DMET != TRUE]

# As can be seen in the table above `r nrow(dtMAPPING[DMET == TRUE])` 
# double entries exist.  
# These will be excluded from further analysis.
```

### SAP Article - DUPLICATE CHECK ###

In order to check if any SAP Articles are set up twice a check on the relationship 
between SAP Article and the supplier EAn (EANTP = HE) is done.  In case multiple 
Articles share the same EAN these articles are said to be duplicates. 

```{r SAP_DUPLICATES, echo=fECHO, results=fRESULTS}
dtMAPPING <- dtMAPPING[EANTP == "HE"
                       , SAPDUP := duplicated(dtMAPPING[EANTP == "HE"], 
                                              by = c("EAN11"))]
dtMAPPING <- dtMAPPING[EANTP == "HE", 
                       D002 := sum(SAPDUP), by = c("EAN11")]
table(dtMAPPING[EANTP == "HE"]$SAPDUP)
tmp <- dtMAPPING[D002 > 0][order(EAN11),
                           .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)]
(tmp[1:10])

fileName  <- "./RESULTS/SAP_ARTICLE_DUPLICATES.csv"
write.table(dtMAPPING[D002 > 0][order(EAN11), 
                .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
            file = fileName, 
            sep = ";",col.names = TRUE, row.names = FALSE)

write.xlsx(dtMAPPING[D002 > 0][order(EAN11), 
                .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
           fileXL, sheetName="SAP_ARTICLE_DUPLICATES", 
           col.names=TRUE, row.names=FALSE, append=FALSE, showNA=TRUE)

dtMAPPING <- dtMAPPING[is.na(SAPDUP) | SAPDUP == FALSE]

```

It seems `r nrow(tmp)/2` duplicates exist. These records are excluded from further
analysis.  
Details can be found in the file: `r fileName`


### HPEAN ###

The following table shows a count on EANTP and HPEAN.

```{r HPEAN,echo=fECHO, results=fRESULTS}

(tmp      <- table(dtMAPPING$EANTP, ifelse(is.na(dtMAPPING$HPEAN), "-", "X")))

fileName  <- "./RESULTS/HE_not_HPEAN.csv"
write.table(dtMAPPING[EANTP == "HE" & is.na(HPEAN), 
                      .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
            file = fileName, 
            sep = ";",col.names = TRUE, row.names = FALSE)

write.xlsx(dtMAPPING[EANTP == "HE" & is.na(HPEAN), 
                      .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
           fileXL, sheetName="HE_not_HPEAN", 
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)

dtMAPPING <- dtMAPPING[EANTP != "HE", ]
```

Note there are `r tmp[which(rownames(tmp) == "HE"), colnames(tmp) == "-"]` 
entries with EANTP = HE but which are not marked as HPEAN.  
Details can be found in the file: `r fileName`

The rest of the analysis will focus on the Z* EANTP by excluding HE.

### N:1 Relationship ###

The remaining number of records for analysis are `r  nrow(dtMAPPING)`.  
These distribution per EANTP is as follows:   

```{r RN1_DISTR, echo=fECHO, results=fRESULTS}
table(dtMAPPING$EANTP)
```


Next a check will be done if Multiple SAP Articles are mapped against the same
legacy article (N:1 relationship). This should not happen

```{r RN1, echo=fECHO, results=fRESULTS}
fileName  <- "./RESULTS/RN1.csv"

dtMAPPING <- dtMAPPING[, D_ET := duplicated(dtMAPPING, 
                                            by = c("EAN11", "EANTP"))]
if(sum(dtMAPPING$D_ET) > 0 ){
dtMAPPING <- dtMAPPING[, D001 := sum(D_ET), by = c("EAN11", "EANTP")]
table(dtMAPPING[D_ET == TRUE]$EANTP)
sort(table(dtMAPPING[D001 > 0]$EAN11), decreasing=TRUE)[1:10]

tmp <- dtMAPPING[D_ET == TRUE]

dtMAPPING <- dtMAPPING[ !EAN11 %in% c("DUPLICATE", "DUP")]

rbind(
  dtMAPPING[D001 > 0 & EANTP == "Z1", 
            .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)][1:4],
  dtMAPPING[D001 > 0 & EANTP == "Z2", 
            .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)][1:4],
  dtMAPPING[D001 > 0 & EANTP == "Z3", 
            .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)][1:4]
  )

write.table(dtMAPPING[D001 > 0, .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
            file = fileName, 
            sep = ";",col.names = TRUE, row.names = FALSE)

write.xlsx(dtMAPPING[D001 > 0, .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
           fileXL, sheetName="RN1", 
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)

dtMAPPING <- dtMAPPING[D_ET != TRUE]

# It seems that there are 2 special types which will be excluded from further analysis, being:  
# 1. DUPLICATE  
# 2. DUP  

} else {
  tmp <- NULL
  if (file.exists(fileName)){file.remove(fileName)}
}

dtMAPPING <- dtMAPPING[EANTP %in% c("Z1", "Z2", "Z3")]
```

In total there are `r ifelse(is.null(nrow(tmp)), 0L ,nrow(tmp))` entries.  
All N:1 relationships will be excluded from further analysis.  

Note that Z3 will be kept in the analysis as these are needed for the UK.
  
*'Basically the main purpose of the field is for CL reporting but also applies to 
lenses. When the product team need to run a report on registrations they use 
the CF REG and collection codes CF COL.  
If the EANs aren't migrated then it won’t be possible to report of this split.'*


```{r TEXT, echo=FALSE, results='hide'}
## TEXT ##

# dtMAPPING <- dtMAPPING[, REGEX:= gsub("[0-9]", "", EAN11, ignore.case = TRUE)]
# t001 <- table(dtMAPPING$REGEX)
# (sort(t001, decreasing = TRUE)[1:15])

# The number of legacy aticle numbers which are numeric (so without characters) is: 
# `r t001[which(row.names(sort(t001, decreasing = TRUE)) == "")]`
```


```{r DUPLICATES, echo=FALSE, results='hide'}
## DUPLICATES ##

# dtMAPPING <- dtMAPPING[, DUPLICATE:= grepl("DUPLICATE", EAN11, ignore.case = TRUE)]
# (t00      <- table(dtMAPPING$DUPLICATE))
# dtMAPPING <- dtMAPPING[DUPLICATE == FALSE, ]

# Number of ENA11 with "DUPLICATE": `r t00["TRUE"]`.  
# These records will *not* be taken into account in the rest of theh analysis.
```

# Analysis #  
The table MEAN has now been reduced to `r nrow(dtMAPPING)` rows out of `r nrow(dtMEAN)`.

The distribution per EANTP is as follows:   
```{r RN1_DISTR_EANTP, echo=fECHO, results=fRESULTS}
table(dtMAPPING$EANTP)
```

## One SAP Article being mapped by multiple OPCO's ##

The following table shows the SAP Articles which have legacy Articles in multiple OPCO's.

```{r M__, echo=fECHO, results=fRESULTS}

# Duplicate SAP Articles for the same MEINH
dtMAPPING <- dtMAPPING[, DM__ := duplicated(dtMAPPING, 
                                            by = c("MATNR")                  )]
dtMAPPING <- dtMAPPING[, CM__ := sum(DM__), by = c("MATNR")]
tmp <- dtMAPPING[CM__ > 0][order(MATNR), 
                           .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)]
if (nrow(tmp) > 0){
  (tmp[1:10])
  }

```

In total `r nrow(dtMAPPING[DM__ > 0])` articles are mapped by multiple OPCO's.  
This can be correct.

## One SAP Article having multiple legacy articles (1:N) ##

The following table shows the SAP Articles which have multiple legacy Articles 
mapped for an OPCO.

```{r M_N, echo=fECHO, results=fRESULTS}
# Duplicate entries by SAP Article and OPCO
dtMAPPING <- dtMAPPING[, DM_N := duplicated(dtMAPPING, 
                                            by = c("MATNR", "EANTP")         )]
dtMAPPING <- dtMAPPING[, CM_N := sum(DM_N), by = c("MATNR", "EANTP")]
tmp <- dtMAPPING[CM_N > 0][order(MATNR), 
                           .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)]
if (nrow(tmp) > 0){
  dtMAPPING[, .(SAP  = sum(DM_N), LEG = sum(CM_N), N = .N, 
                R1_N = paste("1", round(sum(CM_N)/sum(DM_N), 0), sep=":")), 
            by=c("EANTP")]
  }

if (nrow(tmp) > 0){
  print(tmp[1:10])
  }

fileName  <- "./RESULTS/R1N.csv"
write.table(dtMAPPING[CM_N > 0, .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
            file = fileName, 
            sep = ";", col.names = TRUE, row.names = FALSE)

write.xlsx(dtMAPPING[CM_N > 0, .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
           fileXL, sheetName="R1N", 
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)

```

In total `r nrow(dtMAPPING[DM_N > 0])` articles have multiple legacy articles mapped.
This is the famous 1:N relationship which makes it difficult to report on legacy 
articles. 

## One SAP Article having multiple legacy articles (1:N) by Article Type##

The following table shows the SAP Articles which have multiple legacy Articles 
mapped for an OPCO split by Article Type.

```{r M_N_AT, echo=fECHO, results=fRESULTS}
# Duplicate entries by SAP Article and OPCO
dtMAPPING <- dtMAPPING[, DM_N_AT := duplicated(dtMAPPING, 
                                               by = c("MATNR", "EANTP")         )]
dtMAPPING <- dtMAPPING[, CM_N_AT := sum(DM_N), by = c("MATNR", "EANTP")]
tmp <- dtMAPPING[CM_N_AT > 0][order(MATNR), 
                              .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)]
if (nrow(tmp) > 0){
  dtMAPPING[, .(SAP  = sum(DM_N_AT), LEG = sum(CM_N_AT), N = .N, 
                R1_N= paste("1", round(sum(CM_N_AT)/sum(DM_N_AT), 0), sep=":")), 
            by=c("EANTP", "MTART", "MTBEZ")][order(EANTP, MTART)]
  }

fileName  <- "./RESULTS/R1N_AT.csv"
write.table(dtMAPPING[CM_N_AT > 0, .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
            file = fileName, 
            sep = ";", col.names = TRUE, row.names = FALSE)

write.xlsx(dtMAPPING[CM_N_AT > 0, .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN) ], 
           fileXL, sheetName="R1N_AT", 
           col.names=TRUE, row.names=FALSE, append=TRUE, showNA=TRUE)
```

# Result #

Below one can see the 1:N relationships per article type excluding the 1:1

```{r Result, echo=fECHO, results=fRESULTS}
if (nrow(tmp) > 0){
  dtMAPPING[, .(SAP  = sum(DM_N_AT), LEG = sum(CM_N_AT), N = .N, 
                R1_N= paste("1", round(sum(CM_N_AT)/sum(DM_N_AT), 0), sep=":")), 
            by=c("EANTP", "MTART", "MTBEZ")][SAP > 0][order(-R1_N, EANTP, MTART)]
  }
```

A sample showing the actual records

```{r RESULT_SAMPLE, echo=FALSE, results=FALSE}
if (nrow(tmp) > 0){
  print(tmp[1:10])
  }
```


```{r ME_, echo=FALSE, results=FALSE}

## Double mapping records ##

# The following table shows if any double entries exist.  
# This should not be the case.

# Duplicate entries were SAP Article and EAN11 is the same
dtMAPPING <- dtMAPPING[, DME_ := duplicated(dtMAPPING, 
                                            by = c("MATNR", "EAN11")         )]
dtMAPPING <- dtMAPPING[, CME_ := sum(DME_), by = c("MATNR", "EAN11")]
tmp <- dtMAPPING[CME_ > 0][order(MATNR), 
                           .(MATNR, MEINH, LFNUM, EAN11, EANTP, HPEAN)]
if (nrow(tmp) > 0) {(tmp[1:10])}

# In total `r nrow(dtMAPPING[DME_ > 0])` articles have double entries.
```


```{r Other, echo=fECHO, results=fRESULTS}

# dtMARM[, TAB:="MARM"]
# dtMEAN[, TAB:="MEAN"]
# 
# dtMAPPING <- dtMEAN[, .(MATNR, EAN11, EANTP, TAB)]
# setnames(dtMAPPING, "EANTP", "NUMTP")
# 
# dtMAPPING <- rbind(dtMAPPING, dtMARM[, .(MATNR, EAN11, NUMTP, TAB)])
# setkey(dtMAPPING, "MATNR", "TAB", "NUMTP")
# dtMAPPING <- dtMAPPING[EAN11!="DUPLICATE",]


# dtMAPPING[, DM__ := duplicated(dtMAPPING, by=c("MATNR"))]
# dtMAPPING[, DME_ := duplicated(dtMAPPING, by=c("MATNR","EAN11"))]
# dtMAPPING[, DMEN := duplicated(dtMAPPING, by=c("MATNR","EAN11","NUMTP" ))]
# dtMAPPING[, DM_N := duplicated(dtMAPPING, by=c("MATNR","NUMTP" ))]
# 
# dtMAPPING[, D001 := sum(DMEN), by=c("MATNR","NUMTP")]
# dtMAPPING[, D002 := sum(DM_N), by=c("MATNR","NUMTP")]
# 
# dtCHK001 <- dtMAPPING[D001  > 0]
# dtCHK002 <- dtMAPPING[D001 == 0 & D002 > 0]
# 
# dtCHK003 <- dtMAPPING[D001 == 0 & D002 > 0 & NUMTP == "HE"]
# 
# dtCHK004 <- dtCHK001[DM__ & DME_ & DMEN & DM_N,]
# dtMAT_Z1 <- dtCHK004[NUMTP == "Z1", ]
# 
# 
# dtCHK006 <- dtGVBNL
# setnames(dtCHK006, "article_number", "EAN11")
# 
# 
# dtMAT_Z1[, D_E_ := duplicated(dtMAT_Z1, by=c("EAN11"))]
# setkey(dtMAT_Z1, "EAN11")
# setkey(dtMAT_Z1, "MATNR", "TAB", "NUMTP")
# dtMAT_Z1 <- dtMAT_Z1[D_E_ != TRUE, ]
# 
# dtCHK007 <- merge(dtCHK006, dtMAT_Z1[,.(EAN11, MATNR)], by="EAN11", all.x=TRUE)
```


